### 2020-10-27 reports/article.tex
addressing Perrine's comments

% title goes here:
\begin{flushleft}
{\Large Spatially-explicit simulation of urban heat mitigation by increasing the tree canopy cover
\textbf\newline{}
}
\newline
% authors go here:
\\
Mart\'i Bosch\textsuperscript{*},
% Maxence Locatelli,
% J\'er\^ome Chenal
\\
\bigskip
Urban and Regional Planning Community (CEAT), \'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Lausanne, Switzerland
\\ 
\bigskip
* Corresponding author: marti.bosch@epfl.ch

@@

@@

Urbanization is nowadays a global phenomenon that is increasingly concentrating the world's population in urban areas, which are expected to grow in both the number of dwellers and spatial extent \cite{seto2011meta, angel2012atlas, unitednations2018world}.
As a major force of landscape change, urbanization is characterized by the conversion of natural to artificial surfaces, which alters the energy and water exchanges as well as the movement of air. Such changes often result in the urban heat island (UHI) effect, a phenomenon by which urban temperatures are warmer than its rural surroundings \cite{oke1973city,oke1982energetic,arnfield2003two,voogt2003thermal,grimmond2007urbanization,phelan2015urban}. % \cite{oke1982energetic}.

% The negative impacts of UHI have been widely documented and include increased water and energy consumption \cite{santamouris2015impact}, reduced productivity \cite{kjellstrom2009workplace} and increased health risks \cite{kovats2008heat,laaidi2012impact}.
The negative impacts of UHI have been widely documented and include increased energy and water consumption \cite{akbari2001cool,golden2006energy,santamouris2015impact}, reduced workplace productivity \cite{kjellstrom2009workplace,zander2015heat} and aggravation of health risks \cite{chestnut1998analysis,kovats2008heat,laaidi2012impact}.
% As urban areas grow and global temperatures increase, heat waves are expected to become more intense and frequent ant the UHI effect
As urban areas grow and global temperatures rise, the UHI effect is expected to become more intense \cite{meehl2004more,huang2019projecting}, which makes urban heat mitigation a major priority for urban planning and policy-making.
% Green infrastructure
% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation, nevertheless, the impacts of the urban tree canopy on air temperature show a complex spatial behaviour that remains poorly understood \cite{bowler2010urban,phelan2015urban,koc2018evaluating}.
Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.

The present work introduces a novel approach to spatially evaluate the heat mitigation potential that could be achieved by increasing the urban tree canopy cover. The proposed method consists of three major parts.
% 1. Couple the cadastral LULC map with a high-resolution tree canopy map to detect locations where the tree canopy cover can be increased
% 2. Generate a variety of synthetic scenarios by increasing the tree canopy cover, which can mimic urban greening strategies. % in different spatial configurations
% 3. 
First, the cadastral LULC map is coupled with a high-resolution tree canopy map to detect candidate pixels where the tree canopy cover can be increased.
Secondly, a synthetic scenario is generated by increasing the tree canopy cover in a fraction of the candidate pixels --- the quantity of transformed pixels can be set exogenously, e.g., to mimic available budgets and resources.
The transformed pixels can be selected from the candidate pixels by randomly sampling, or pursuing specific spatial configurations by scattering or clustering them to other pixels with high tree canopy cover.
% is applied with the LULC map that corresponds to 
% Finally, the synthetic LULC map of each scenario is fed to the InVEST urban cooling model in order to estimate the air temperature of
Finally, the spatial distribution of air temperature of each scenario is estimated by applying the InVEST urban cooling model to the corresponding synthetic LULC map.
By applying such a procedure in the urban agglomeration of Lausanne, Switzerland, this study aims to map the heat mitigation potential that can be achieved departing from the existing urban fabric.
In order to quantify the effects of the abundance and spatial configuration of the tree canopy cover on urban heat mitigation, a set of synthetic scenarios are generated by increasing different proportions of tree canopy cover in distinct spatial configurations. % and human thermal comfort
% The latter is achieved by coupling a gridded population census with the temperature maps simulated with different proportions and spatial configurations of tree canopy cover.
Additionally, the human thermal comfort of each scenario is evaluated by coupling the simulated temperature map with a gridded population census.
% TODO: the aim is to do something that helps planning
% The results

@@

In order to evaluate the human thermal comfort, the population data for the study area has been extracted from the population and households statistics (STATPOP) \cite{sfso2020statistique} provided at a 100~m resolution by the Swiss Federal Statistical Office (SFSO) with the Python library swisslandstats-geopy \cite{bosch2019swisslandstats}.

@@

The spatial distribution of UHI is simulated with the InVEST urban cooling model (version 3.8.0) \cite{sharp2020invest}, which is based on the heat mitigation provided by shade, evapotranspiration and albedo. The main inputs are a LULC raster map, a reference evapotranspiration raster and a biophysical table containing model information of each LULC class of the map. Each row of the biophysical table represents a LULC class, and features the following columns:

\begin{itemize}
\item \texttt{lucode} the LULC class code as represented in the LULC raster map
\item \texttt{Shade} a value between 0 and 1 representing the proportion of tree canopy cover in such LULC class
\item \texttt{Kc} the evapotranspiration coefficient
\item \texttt{Albedo} a value between 0 and 1 representing the proportion of solar radiation directly reflected by the LULC class
\item \texttt{Green\_area} whether the LULC class should be considered a green area
% \item \texttt{Building\_intensity} a value between 0 and 1 representing the ratio between floor area and land area
\end{itemize}

In order to simulate the spatial distribution of air temperature ($T_{air}$), the model requires two additional inputs. The first is the rural reference temperature $T_{ref}$, where the UHI effect is not observed, e.g., in the rural surroundings of the city. The second is the magnitude of the urban heat island effect $UHI_{max}$, namely the difference between the rural refrence temperature and the maximum $T_{air}$ observed in the city center.

The data inputs described above are then used to compute the cooling capacity index, which is based on the physical mechanisms that contribute to cooling urban temperatures. More precisely, the cooling capacity index used in InVEST urban cooling model builds upon the indices proposed by Zardo et al. \cite{zardo2017estimating}, which are based on shading and evapotranspiration, and extends them by adding a factor to account for the albedo.
For each pixel $i$ of the LULC raster map, the cooling capacity index is computed as in:

\begin{equation}
  \label{eq:cooling-capacity}
  CC_i = w_{S} \cdot \textrm{S}_i + w_{AL} \cdot \textrm{AL}_i + w_{ET} \cdot \textrm{ETI}_i
\end{equation}

where $S_i$, $AL_i$ and $ETI_i$ respectively represent the tree shading, albedo and evapotranspiration values of pixel $i$ as defined in the biophysical table, and $w_{S}$, $w_{AL}$ and $w_{ET}$ represent the weights attributed to each component respectively.
The values of $S_i$ and $AL_i$ are retrieved from the biophysical table according to the LULC class of the pixel $i$ (see \autoref{tab:biophysical-table}), whereas the reference evapotranspiration $ETI_i$ pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum $T_{air}$ values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation} (see Bosch et al. \cite{bosch2020spatially} for more details on the estimation of $ETI_i$).
% The values of $S_i$ and $AL_i$ are retrieved from the biophysical table according to the post-refinement LULC class of the pixel $i$, e.g., the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \ref{sec:biophysical-table}). On the other hand, the reference evapotranspiration $ETI_i$ pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum $T_{air}$ values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation} (see Bosch et al. \cite{bosch2020spatially} for more details on the estimation of $ETI_i$).

In order to account for the cooling effect of large green spaces, the computed cooling capacity index of pixels that are part of large green areas ($>$ 2~ha) is adjusted as in:

\begin{equation}
  \label{eq:cooling-capacity-green}
  CC_i^{green} = \sum_{j \in \Omega_i} g_i \cdot CC_j \cdot e^{-\frac{d(i, j)}{d_{cool}}}
\end{equation}

where $g_i$ is 1 when the pixel $i$ is a green area and 0 otherwise (as defined in the biophyisical table), $d(i, j)$ is the distance between pixels $i$ and $j$, $d_{cool}$ is a parameter that defines the distance over which a green space has a cooling effect, and $\Omega_i$ is the set of pixels whose distance to $i$ is lower than $d_{cool}$.

Then, a heat mitigation index is computed as:

% $\; if \;\; i \; \textrm{is part of a large green area} \;\; or \;\; CC_i > CC_i^{green}$
% $\; otherwise$
\begin{equation}
  \label{eq:heat-mitigation index}
  HM_i=\begin{cases}
    CC_i & if \; i \in \textrm{large green area} \;\; or \;\; CC_i > CC_i^{green} \\
    CC_i^{green} & otherwise \\
  \end{cases}
\end{equation}

which is employed to compute the $T_i$ for each pixel $i$ of the study area as in:

\begin{equation}
  \label{eq:tair-nomix}
  T_i^{no \, mix} = T_{ref} + (1 - HM_i) \cdot UHI_{max}
\end{equation}

where $T_{ref}$ and $UHI_{max}$ are the rural reference temperature and the magnitude of the UHI effect respectively, as described above.
Finally, the $T_{air}$ values of each pixel $T_i^{no \, mix}$ are spatially averaged using a Gaussian function with a kernel radius $r$ defined by the user.

Following the calibration of the model to the same study area by Bosch et al. \cite{bosch2020spatially}, the values of the cooling capacity weights have been set to $w_{S} = 0.59$, $w_{AL} = 0.24$ and $w_{ET} = 0.17$, the distance over which green spaces have a cooling effect $d_{cool}$ and the air mixing radius $r$ have been set to 89.21 and 236.02~m respectively.
The $T_{ref}$ and $UHI_{max}$ values have been set based on the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ has been set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ has been set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

@@

% The reclassification procedure consists of three steps.
% % First, for each LULC class, the set of 10m pixels of such class is coupled with the tree canopy and building masks
% Firstly, each 10~m pixel is coupled with the tree canopy and building masks in order to respectively compute its proportion of tree and building cover.
% % Secondly, each LULC class is further refined into a set of subclasses depending on the joint distribution of tree cover and building cover of its 10~m pixels, e.g., the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''. %  its set of 10~m pixels are % the 10m pixels of each LULC class are grouped into equally-spaced bins according to their proportion of tree cover
% Secondly, the set of 10~m pixels of each LULC class are grouped into a set of bins to form two histograms, one based on their proportion of tree cover and the other analogously for the building cover.
% % which groups the 10~m pixels of each LULC class into an increasing number of equally-spaced bins according to their proportion of tree cover, until adding an extra bin results in having a bin whose number of samples is lower than certain threshold.
% The number of bins is determined by means of an iterative procedure which distributes the 10~m pixels into an increasing number of equally-spaced bins until adding an extra bin results in having a bin whose number of samples is lower than certain threshold.
% After empirical exploration, a threshold value of 3~\% has been manually chosen with the aim of obtaining a set of refined LULC codes that can be interpreted easily.
% % cartesian product
% Finally, the two histograms are joined so that each LULC class is further refined into a set of subclasses, e.g., the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''.
The reclassification procedure consists of three steps.
Firstly, each 10~m pixel is coupled with the tree canopy and building masks in order to respectively compute its proportion of tree and building cover.
Secondly, the set of 10~m pixels of each LULC class are grouped into a user-defined set of bins to form two histograms, one based on their proportion of tree cover and the other analogously for the building cover.
% cartesian product
Finally, the two histograms are joined so that each LULC class is further refined into a set of classes. For example, if two bins were used for both the tree and building cover, the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''.
In the present work, four equally spaced bins (i.e., distinguishing 0-25\%, 25-50\%, 50-75\% and 75-100\% intervals) have been used to reclassify each LULC class according to both the tree and building cover.

In order to adapt the biophysical table of the InVEST urban cooling model to the reclassified LULC classes, the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \autoref{tab:biophysical-table}).

@@

% One of the main advantages of using models based on biophysical mechanisms is that they allow for reasonable
% Departing from the refined LULC map, a set of synthetic scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
% More precisely, in order to mimic scenarios of urban greening, pixels whose base LULC class corresponds to roads, sidewalks, traffic islands and other impervious surfaces will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
Departing from the refined LULC map, a set of urban greening scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, pixels whose base LULC class corresponds to ``building'', ``road, path'', ``sidewalk'', ``traffic island'', ``other impervious'' and ``garden'' will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
% limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100~\%
In order to ensure that such an increase of the tree canopy cover is performed only where the existing urban fabric permits it, the transformed pixels . First, the transformations might only take place in pixels where the proportion of building cover is under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown. Secondly, pixels of the ``road, path'' class might only be transformed when they are next to a pixel of a different class, which prevents increasing the tree canopy cover in pixels that are in the middle of a road (e.g., a highway).

>>>>

% title goes here:
\begin{flushleft}
{\Large Spatially-explicit simulation of urban heat mitigation by increasing the tree canopy cover
\textbf\newline{}
}
\newline
% authors go here:
\\
Mart\'i Bosch\textsuperscript{1,*},
Maxence Locatelli\textsuperscript{1},
Perrine Hamel\textsuperscript{2},
R\'emi Jaligot\textsuperscript{1},
J\'er\^ome Chenal\textsuperscript{1},
St\'ephane Joost\textsuperscript{3}
\\
\bigskip
\bf{1} Urban and Regional Planning Community, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
\\ 
\bf{2} Asian School of the Environment, Nanyang Technological University, Singapore
\\
\bf{3} Laboratory of Geographic Information Systems, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
\\
\bigskip
\bf{*} Corresponding author: marti.bosch@epfl.ch

@@

% Urban green space, especially trees, can contribute to the reduction of urban temperatures in extreme heat events.
Urban green infrastructure, especially trees, are widely regarded as one of the most effective ways to reducing urban temperatures in extreme heat events, and alleviate its adverse impacts on human health and well-being.
% Nevertheless, the effect of the spatial pattern on urban temperatures.
Nevertheless, urban planners and decision-makers are still lacking methods and tools to spatially assess the cooling effects of urban green spaces and exploit them to assess greening strategies at the urban agglomeration scale.
This article introduces a novel spatially-explicit approach to simulate urban greening scenarios by increasing the tree canopy cover in the existing urban fabric, and evaluating their heat mitigation potential.
The latter is achieved by applying the InVEST urban cooling model to the synthetic land use/land cover maps generated for the greening scenarios.
An case study in the urban agglomeration of Lausanne, Switzerland, experiments with a range of tree canopy increases in distinct spatial configurations, and shows a potential alleviation of the urban nighttime temperatures of up to 2$\degree$C.
The spatial pattern of the tree canopy strongly influences the human exposure to the highest temperatures, and small increases in the abundance of tree canopy cover with the appropriate spatial configuration can have major impacts on human health and well-being.
% This article
The proposed approach can serve to support urban planning and design adaptative solutions to enhance climate resilience.

@@

Urbanization is a global phenomenon that increasingly concentrates the world's population in urban areas, with the latter expected to grow in both the number of dwellers and spatial extent over the next decades \cite{seto2011meta, angel2012atlas, unitednations2018world}.
As a major force of landscape change, urbanization is characterized by the conversion of natural to artificial surfaces, which alters the energy and water exchanges as well as the movement of air. Such changes often result in the urban heat island (UHI) effect, a phenomenon by which urban temperatures are warmer than its rural surroundings \cite{oke1973city,oke1982energetic,arnfield2003two,voogt2003thermal,grimmond2007urbanization,phelan2015urban}. % \cite{oke1982energetic}. 
% The negative impacts of UHI have been widely documented and include increased water and energy consumption \cite{santamouris2015impact}, reduced productivity \cite{kjellstrom2009workplace} and increased health risks \cite{kovats2008heat,laaidi2012impact}.
The negative impacts of UHI have been widely documented and include increased energy and water consumption \cite{akbari2001cool,golden2006energy,santamouris2015impact}, reduced workplace productivity \cite{kjellstrom2009workplace,zander2015heat} and aggravation of health risks \cite{chestnut1998analysis,kovats2008heat,laaidi2012impact}.
% As urban areas grow and global temperatures increase, heat waves are expected to become more intense and frequent ant the UHI effect
As urban areas grow and global temperatures rise, the UHI effect is expected to become more intense \cite{meehl2004more,huang2019projecting}, which makes urban heat mitigation a major priority for urban planning and policy-making \cite{geneletti2020planning}.
% Green infrastructure

% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation, nevertheless, the impacts of the urban tree canopy on air temperature show a complex spatial behaviour that remains poorly understood \cite{bowler2010urban,phelan2015urban,koc2018evaluating}.
% Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.
% Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain.
% TODO: While many case studies have reproted strong evidence of the heat mitigation of urban green space, e.g., cooling effects of parks, very few studies have attempted to model such effects in space so that synthetic scenarios can be evaluated
% TODO: from the ecosystem service perspective, there is a need to consider green space development for the entire urban region \cite{lin2013sharing,haaland2015challenges,artmann2019urban}
While many case studies have reported evidence of the cooling effects of urban green areas, the relationship between their size and their cooling capacity is non-linear \cite{zardo2017estimating}, and little is known about how the overall spatial configuration of urban green spaces affects the heat mitigation at the urban agglomeration scale \cite{lin2013sharing,jim2013sustainable,haaland2015challenges,artmann2019urban}.
% TODO: case studies might be hard to generalize, e.g., effects of the background climate \cite{zhou2017effects}, \cite{yu2018strong,wang2020significant}.
% Additionally, the effects configuration of urban green space on heat mitigation are strongly mediated by the background climate of the region of study \cite{zhou2017effects,yu2018strong,wang2020significant}.
% what is the gap that we are addressing: there have not been fine-grained evaluations of the effect of increasing the tree canopy in realistic settings.
Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain, largely because of the lack of fine-grained approaches to evaluate the cooling effects of the spatial pattern of the tree canopy at the urban agglomeration scale. % , which consider the existing urban fabric and local environmental context.

% The present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
With the aim of addressing the above shortcomings, the present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
The proposed method consists of two major parts.
% 1. Couple the cadastral LULC map with a high-resolution tree canopy map to detect locations where the tree canopy cover can be increased
% 2. Generate a variety of synthetic scenarios by increasing the tree canopy cover, which can mimic urban greening strategies. % in different spatial configurations
% 3.
% First, a land use/land cover map is coupled with a high-resolution tree canopy map to detect candidate pixels where the tree canopy cover can be increased.
% Secondly, a synthetic scenario is generated by increasing the tree canopy cover in a fraction of the candidate pixels --- the quantity of transformed pixels can be set exogenously, e.g., to mimic available budgets and resources.
% The transformed pixels can be selected from the candidate pixels by randomly sampling, or pursuing specific spatial configurations by scattering or clustering them to other pixels with high tree canopy cover.
% % Finally, the synthetic LULC map of each scenario is fed to the InVEST urban cooling model in order to estimate the air temperature of
% Finally, the spatial distribution of air temperature of each scenario is estimated by applying the InVEST urban cooling model to the corresponding synthetic LULC map.
% Given the candidate locations where the tree canopy can be increased, which can be mapped from land use/land cover (LULC) data and high-resolution tree canopy maps, a set
% First, given the candidate locations where the tree canopy can be increased in an existing urban fabric,
First, synthetic scenarios are generated by increasing the tree canopy cover in candidate locations where the existing urban fabric permits it. % In order to explore the effects of the abundance and A set of 
% is applied with the LULC map that corresponds to
Then, the spatial distribution of air temperature of each synthetic scenario is estimated with the InVEST urban cooling model, which simulates urban heat mitigation based on three biophysical processes, namely shade, evapotranspiration and albedo. % which simulates urban heat mitigation based on the shade, evapotranspiration and albedo of the urban fabric.
By applying such a procedure in the urban agglomeration of Lausanne, Switzerland, this study aims to map the heat mitigation potential that can be achieved departing from the existing urban fabric.
In order to quantify the effects of the abundance and spatial configuration of the tree canopy cover on urban heat mitigation, a set of synthetic scenarios are generated by increasing different proportions of tree canopy cover in distinct spatial configurations. % and human thermal comfort
% The latter is achieved by coupling a gridded population census with the temperature maps simulated with different proportions and spatial configurations of tree canopy cover.
Additionally, the human exposure to urban heat is evaluated in each scenario by coupling the simulated temperature map with a gridded population census.
% TODO: the aim is to do something that helps planning
% The results

@@

In order to evaluate the human exposure to UHI, the population data for the study area has been extracted from the population and households statistics (STATPOP) \cite{sfso2020statistique} provided at a 100~m resolution by the Swiss Federal Statistical Office (SFSO) with the Python library swisslandstats-geopy \cite{bosch2019swisslandstats}.

@@

The spatial distribution of air temperatures is simulated with the InVEST urban cooling model (version 3.8.0) \cite{sharp2020invest}, which is based on the heat mitigation provided by shade, evapotranspiration and albedo.
The main inputs are a land use/land cover (LULC) raster map, a reference evapotranspiration raster and a biophysical table containing model information of each LULC class of the map.
% A detailed overview of the model can be found in its user guide \cite{sharp2020invest} as well as in Bosch et al. \cite{bosch2020spatially}.
% Each row of the biophysical table represents a LULC class, and features the following columns:
% \begin{itemize}
% \item \texttt{lucode} the LULC class code as represented in the LULC raster map
% \item \texttt{Shade} a value between 0 and 1 representing the proportion of tree canopy cover in such LULC class
% \item \texttt{Kc} the evapotranspiration coefficient
% \item \texttt{Albedo} a value between 0 and 1 representing the proportion of solar radiation directly reflected by the LULC class
% \item \texttt{Green\_area} whether the LULC class should be considered a green area
% % \item \texttt{Building\_intensity} a value between 0 and 1 representing the ratio between floor area and land area
% \end{itemize}
The LULC maps have been obtained by rasterizing the vector geometries of the official cadastral survey of the Canton of Vaud \cite{asitvd2018structure} as of August 2019 to a 10~m resolution. Such a dataset distinguishes 25 LULC classes which are relevant ot the urban, rural and wild landscapes encountered in Switzerland.
The reference evapotranspiration pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum air temperature values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation}.
The biophysical table used in this study is shown in \autoref{tab:si-biophysical-table}.
A more thorough description of the model and the data inputs can be found in Bosch et al. \cite{bosch2020spatially}.

% In order to simulate the spatial distribution of $T_{air}$, the model requires two additional inputs. The first is the rural reference temperature $T_{ref}$, where the UHI effect is not observed, e.g., in the rural surroundings of the city. The second is the magnitude of the urban heat island effect $UHI_{max}$, namely the difference between the rural refrence temperature and the maximum $T_{air}$ observed in the city center.
% $d_{cool}$ is a parameter that defines the distance over which a green space has a cooling effect, and $\Omega_i$ is the set of pixels whose distance to $i$ is lower than $d_{cool}$.
% Finally, the $T_{air}$ values of each pixel $T_i^{no \, mix}$ are spatially averaged using a Gaussian function with a kernel radius $r$ defined by the user.
% Following the calibration of the model to the same study area by Bosch et al. \cite{bosch2020spatially}, the values of the cooling capacity weights have been set to $w_{S} = 0.59$, $w_{AL} = 0.24$ and $w_{ET} = 0.17$, the distance over which green spaces have a cooling effect $d_{cool}$ and the air mixing radius $r$ have been set to 89.21 and 236.02~m respectively.

The parameters of the model have been set based on its calibration to the same study area by Bosch et al. \cite{bosch2020spatially}.
Finally, the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) values have been set based on the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ has been set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ has been set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

@@

% The reclassification procedure consists of three steps.
% % First, for each LULC class, the set of 10m pixels of such class is coupled with the tree canopy and building masks
% Firstly, each 10~m pixel is coupled with the tree canopy and building masks in order to respectively compute its proportion of tree and building cover.
% % Secondly, each LULC class is further refined into a set of subclasses depending on the joint distribution of tree cover and building cover of its 10~m pixels, e.g., the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''. %  its set of 10~m pixels are % the 10m pixels of each LULC class are grouped into equally-spaced bins according to their proportion of tree cover
% Secondly, the set of 10~m pixels of each LULC class are grouped into a set of bins to form two histograms, one based on their proportion of tree cover and the other analogously for the building cover.
% % which groups the 10~m pixels of each LULC class into an increasing number of equally-spaced bins according to their proportion of tree cover, until adding an extra bin results in having a bin whose number of samples is lower than certain threshold.
% The number of bins is determined by means of an iterative procedure which distributes the 10~m pixels into an increasing number of equally-spaced bins until adding an extra bin results in having a bin whose number of samples is lower than certain threshold.
% After empirical exploration, a threshold value of 3~\% has been manually chosen with the aim of obtaining a set of refined LULC codes that can be interpreted easily.
% % cartesian product
% Finally, the two histograms are joined so that each LULC class is further refined into a set of subclasses, e.g., the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''.
The reclassification procedure consists of three steps.
Firstly, each 10~m pixel is coupled with the tree canopy and building masks in order to respectively compute its proportion of tree and building cover.
Secondly, the set of 10~m pixels of each LULC class are grouped into a user-defined set of bins to form two histograms, one based on their proportion of tree cover and the other analogously for the building cover.
% cartesian product
Lastly, the two histograms are joined so that each LULC class is further refined into a set of classes. For example, if two bins were used for both the tree and building cover, the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''.

In the present work, four equally spaced bins (i.e., distinguishing 0-25\%, 25-50\%, 50-75\% and 75-100\% intervals) have been used to reclassify each LULC class according to both the tree and building cover.
Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.
Therefore, adjacent pixels with a tree canopy cover over 75\% can 
Finally, in order to adapt the biophysical table of the InVEST urban cooling model to the reclassified LULC classes, the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \autoref{tab:si-biophysical-table}).

@@

% \subsubsection*{Mapping candidate pixels}  %  where the tree canopy cover can be increased
% One of the main advantages of using models based on biophysical mechanisms is that they allow for reasonable
% Departing from the refined LULC map, a set of synthetic scenarios will be simulated by altering the LULC classes of certain pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
% More precisely, in order to mimic scenarios of urban greening, pixels whose base LULC class corresponds to roads, sidewalks, traffic islands and other impervious surfaces will be changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' would be changed to ``sidewalk with high tree/low building cover''.
Departing from the refined LULC map, a set of urban greening scenarios will be simulated by altering the LULC classes of certain candidate pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, pixels whose base LULC class corresponds to ``building'', ``road, path'', ``sidewalk'', ``traffic island'', ``other impervious'' and ``garden'' are changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' are be changed to ``sidewalk with high tree/low building cover''.
% limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100\%
In order to ensure that such an increase of the tree canopy cover is performed only where the existing urban fabric permits it, pixels might only be transformed when two conditions are met.
% First, the transformations might only take place in pixels where the proportion of building cover is under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
First, the proportion of building cover in the candidate pixels must be under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
% \footnote{Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.}
Secondly, pixels of the ``road, path'' class might only be transformed when they are adjacent to a pixel of a different class, which prevents increasing the tree canopy cover in pixels that are in the middle of a road (e.g., a highway).
